General purpose gene annotation using deep learning

### 2020-02-10 paper/main.tex
minor
added some stats

\begin{table}[!t]
\processtable{Data group statistics for all data\label{Tab:statistics_all}} {
\begin{tabular}{@{}lll@{}}
\toprule & EnsemblMetazoa & JGI Phytosome\\
\midrule
Fraction of classes  & 0.6, 0.02, 0.1, 0.2 & 0.6, 0.02, 0.1, 0.2 \\
(Intergenic, UTR, CDS, Intron) & & \\
Geenuff error rate & 0.1 (+- 0.02) & 0.3 (+- 0.02) \\
Average genome size in Gbp& 1.1 (+- 0.5) & 0.3 (+- 0.1) \\
Average gene length & 23000 (+- 5000) & 3370 (+- 50) \\
\botrule
\end{tabular}}{Values are averages across all genomes of a data group. The genome size is excluding FASTA sequences without a gene and subsequences that were masked as completely erroneous.}
\end{table}

\begin{table}[!t]
\processtable{Data group statistics for our training data\label{Tab:statistics_training}} {
\begin{tabular}{@{}lll@{}}
\toprule & EnsemblMetazoa & JGI Phytosome\\
\midrule
Fraction of classes  & 0.6, 0.02, 0.1, 0.2 & 0.6, 0.02, 0.1, 0.2 \\
(Intergenic, UTR, CDS, Intron) & & \\
Geenuff error rate & 0.1 (+- 0.02) & 0.3 (+- 0.02) \\
Average genome size in Gbp& 1.1 (+- 0.5) & 0.3 (+- 0.1) \\
Average gene length & 23000 (+- 5000) & 3370 (+- 50) \\
\botrule
\end{tabular}}{Values are averages across all genomes of a data group. The genome size is excluding FASTA sequences without a gene and subsequences that were masked as completely erroneous.}
\end{table}

>>>>

\begin{table}[!t]
\processtable{Data group statistics for all data\label{Tab:statistics_all}} {
\begin{tabular}{@{}lll@{}}
\toprule & Animals & Plants\\
\midrule
Average genome size in Gbp& 1.1 (+- 0.5) & 0.3 (+- 0.1) \\
Average gene length & tbd & tbd \\
Geenuff error rate & tbd & tbd \\
Fraction of class Intergenic  & 0.777 (+- 0.042) & 0.799 (+- 0.089) \\
Fraction of class UTR & 0.006 (+- 0.006) & 0.017 (+- 0.016) \\
Fraction of class CDS & 0.016 (+- 0.014) & 0.085 (+- 0.071) \\
Fraction of class Intron & 0.201 (+- 0.035) & 0.099 (+- 0.057) \\
\botrule
\end{tabular}}{Values are averages of the individual values of each genome in a data group. All statistics except the average gene lengths are excluding FASTA sequences without a gene and subsequences that were masked as completely erroneous. Each strand of DNA was counted seperately. The standart deviation is shown in the brackets.}
\end{table}

\begin{table}[!t]
\processtable{Data group statistics for our training data\label{Tab:statistics_training}} {
\begin{tabular}{@{}lll@{}}
\toprule & Animals & Plants\\
\midrule
Average genome size in Gbp& 2.489 (+- 2.073) & 0.914 (+- 0.934) \\
Average gene length & tbd & tbd \\
Geenuff error rate & tbd & tbd \\
Fraction of class Intergenic & 0.752 (+- 0.05) & 0.808 (+- 0.106) \\
Fraction of class UTR & 0.013 (+- 0.011) & 0.033 (+- 0.023) \\
Fraction of class CDS & 0.028 (+- 0.028) & 0.077 (+- 0.052) \\
Fraction of class Intron  & 0.207 (+- 0.023) & 0.083 (+- 0.037) \\
\botrule
\end{tabular}}{Values are averages of the individual values of each genome in a data group. All statistics except the average gene lengths are excluding FASTA sequences without a gene and subsequences that were masked as completely erroneous. Each strand of DNA was counted seperately. The standart deviation is shown in the brackets.}
\end{table}
